### 2016-01-28 mcmc.tex
problems

@@

\begin{problem}
Why, in \problemname~\ref{prob:firstMH}, did we give the proposal
distribution $q(x'\given x)$ zero mean?
What would be bad if we hadn't done that?
Try setting the mean of $q(x'\given x)$ to something non-zero and see
what happens.
\end{problem}

@@

>>>>

\begin{problem}\label{prob:twod}
Re-do \problemname~\ref{prob:firstMH} but now with an input density
that is a function of two variables $(x, y)$.
For the function use a covariant Gaussian density with variance tensor HOGG,
and then a top-hat function that is uniform on HOGG and zero elsewhere.
For the proposal distribution $q(x'\given x)$ a two-dimensional Gaussian
density with zero mean and variance tensor set to the two-dimensional
identity matrix.
Plot the two one-dimensional histograms and also a two-dimensional scatter
plot for each sampling.
\end{problem}

@@

\begin{problem}
Why, in \problemname~\ref{prob:firstMH}, did we give the proposal
distribution $q(x'\given x)$ zero mean?
What would be bad if we hadn't done that?
Try setting the mean of $q(x'\given x)$ to something non-zero and see
what happens.
Bonus points: Modify the acceptance--rejection criterion to deal with
the messed-up $q(x'\given x)$ and show that everything works once
again.
\end{problem}

@@

\begin{problem}
Look at the source code of HOGG: REFERENCE EMCEE, and see if you can
re-code or extract the autocorrelation-time estimator called HOGG.
This code should take a MCMC chain of parameter vectors as input and
return a vector of autocorrelation times as output.
\end{problem}

\begin{problem}
Run the MCMC sampling of \probemname~\ref{prob:twod} to...HOGG
\end{problem}
